% !TeX root = ./weekly-report-02-23-21.tex
\documentclass[12pt]{article}
% \usepackage{fullpage}
\usepackage{epic}
\usepackage{eepic}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{algorithm,algorithmic}
\usepackage{tikz}
\usepackage{xcolor,colortbl}
\usepackage{wrapfig}
\usepackage{float}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is FULLPAGE.STY by H.Partl, Version 2 as of 15 Dec 1988.
% Document Style Option to fill the paper just like Plain TeX.

\typeout{Style Option FULLPAGE Version 2 as of 15 Dec 1988}

\topmargin 0pt
\advance \topmargin by -\headheight
\advance \topmargin by -\headsep

\textheight 8.9in

\oddsidemargin 0pt
\evensidemargin \oddsidemargin
\marginparwidth 0.5in

\textwidth 6.5in
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagestyle{empty}
\setlength{\oddsidemargin}{0in}
\setlength{\topmargin}{-0.8in}
\setlength{\textwidth}{6.8in}
\setlength{\textheight}{9.5in}


\def\ind{\hspace*{0.3in}}
\def\gap{0.1in}
\def\bigap{0.25in}
\newcommand{\Xomit}[1]{}


\begin{document}

\setlength{\parindent}{0in}
\addtolength{\parskip}{0.1cm}
\setlength{\fboxrule}{.5mm}\setlength{\fboxsep}{1.2mm}
\newlength{\boxlength}\setlength{\boxlength}{\textwidth}
\addtolength{\boxlength}{-4mm}
\begin{center}\framebox{\parbox{\boxlength}{{\bf
MENG PROJECT, FA20\hfill Slang Full Stack Development}\\
% TODO: fill in your own name, netID, and collaborators
Name: Jonathan Gao\hfill 
NetID: jg992
}}
\end{center}
\vspace{2mm}

As of this week, I've moved on from the Linux Kernel project and am moving forward with a new project. For my new project, I will be building the back-end to an app called Slang. Slang is a friend discovery platform that allows friends to meet new people. The main feature of this app is the use of a queue system similar to those found in competitive multiplayer games, where players can queue with friends and teammates as a team. Slang aims to build on this idea, allowing groups of friends to queue together to find other groups of friends to meet. Along with some event suggestions, the app focuses around an effective matching algorithm. Whereas many dating apps nowadays use a ranking algorithm, Slang will be focused around a matching algorithm focused around a detailed profile. 

As for scope, I will still need to go through and define a goal for where the app will get within this semester. Because I am the sole developer at the moment, I may need to spend some time learning front-end development for testing. However, I will be primarily focused on back-end development for my work. 

There are a few problems to define, with this list continuing to grow as we move through the semester. Some of these have rough answers, but I will slowly solidify them as I begin to design the back-end.

\begin{enumerate}
    \item Do groups of friends get matched with one or more groups at a time?
    \item How do we deal with groups of different sizes?
    \item How do we create a profile for a group? or how do we allow multiple people to work on one profile together?
    \item How do we allow for different groups to queue at the same time?
    \item Assuming a noSQL database, how do we store these profiles, matches, and other events?
    \item What kind of data should we collect? How could this data be beneficial in the future?
\end{enumerate}

\end{document}

